Finiteness in Cubical Type Theory

### 2020-06-07 sections/countdown.tex
Update countdown.tex

In this section we will develop a program/proof which can decide countdown
problems totally.
In other words, given a list of numbers and a target, our program will prove
whether a solution exists, and if so, it will provide just that solution.
\section{Classifying The Problem}
So what is a ``solution'' to the countdown problem?
Given some list of numbers, what type classifies the candidates for testing from
those numbers?
What is the type of the following transformation?
\begin{alignat*}{6}
  &1 \; \; \;         &&3         &&7    &&10    &&25  &&50 \\
  &&&3 \times (&&7 \times (&&50 - &&10) - &&25)
\end{alignat*}
Firstly, we can notice that not every number was used in our solution.
So the transformation must information about what to keep and what to discard on
an item-by-item basis: a subsequence, in other words.
% \begin{align*}
%   &1 \; \; \;         &&3         &&7    &&10    &&25  &&50 \\
%   &         &&3         &&7    &&10    &&25  &&50 \\
%   &         &&3         &&7    &&50    &&10  &&25 \\
%   &         &&3   \times      &&7 \times    &&50 -    &&10 -  &&25 \\
%   &&&3 \times ((&&7 \times (&&50 - &&10)) - &&25)
% \end{align*}

  \begin{tikzpicture}

    \node at (-1,  3) {1}  ;
    \node at (0 ,  3) {3}  ;
    \node at (1 ,  3) {7}  ;
    \node at (2 ,  3) {10} ;
    \node at (3 ,  3) {25} ;
    \node at (4 ,  3) {50} ;

    \node at (-1,  1.5) {\xcancel{1}}  ;
    \node at (0 ,  1.5) {3}  ;
    \node at (1 ,  1.5) {7}  ;
    \node at (2 ,  1.5) {10} ;
    \node at (3 ,  1.5) {25} ;
    \node at (4 ,  1.5) {50} ;

    \node(t3)   at (0 ,  0) {3}  ;
    \node(t7)   at (1 ,  0) {7}  ;
    \node(t10)  at (2 ,  0) {10} ;
    \node(t25)  at (3 ,  0) {25} ;
    \node(t50)  at (4 ,  0) {50} ;
    \node(b3)   at (0 , -1.5) {3}  ;
    \node(b7)   at (1 , -1.5) {7}  ;
    \node(b50)  at (2 , -1.5) {50} ;
    \node(b10)  at (3 , -1.5) {10} ;
    \node(b25)  at (4 , -1.5) {25} ;

@@

    \draw[-] (e50.south) -- ++(0.5,-0.75 ) ;
    \draw[-] (e10.south) -- ++(-1 ,-1.5  ) ;
    \draw[-] (e7.south)  -- ++(1.5,-2.25) ;
    \draw[-] (e3.south)  -- ++(2  , -3 ) ;
    \draw[-] (e25.south) -- ++(-2 , -3 ) ;
  \end{tikzpicture}

>>>>

In this section we will develop a program/proof which can decide countdown
problems totally.
In other words, given a list of numbers and a target, our program will prove
whether a solution exists, and if so, it will provide just that solution.
\section{Classifying The Problem}
So what is a ``solution'' to the countdown problem?
Put simply, it is a way to:
\begin{enumerate}
  \item Arrange some or all of the given numbers into a valid expression
  \item Such that the expression, when evaluated, is equal to the target.
\end{enumerate}

What is the type of the following transformation?

Firstly, we can notice that not every number was used in our solution.
So the transformation must information about what to keep and what to discard on
an item-by-item basis: a subsequence, in other words.

\begin{figure}
  \tikzset{>=Triangle[open]}
  \begin{tikzpicture}
    \node (o1)  at (-1, 1.5) { 1} ;
    \node (o3)  at ( 0, 1.5) { 3} ;
    \node (o7)  at ( 1, 1.5) { 7} ;
    \node (o10) at ( 2, 1.5) {10} ;
    \node (o25) at ( 3, 1.5) {25} ;
    \node (o50) at ( 4, 1.5) {50} ;

    \node(t1) at (-1,  0) {\xcancel{1}}  ;
    \node(t3)   at (0 ,  0) {3}  ;
    \node(t7)   at (1 ,  0) {7}  ;
    \node(t10)  at (2 ,  0) {10} ;
    \node(t25)  at (3 ,  0) {25} ;
    \node(t50)  at (4 ,  0) {50} ;

    \draw [-{Rays[n=4]}] (o1.south)  -- (t1.north) ;
    \draw [->] (o3.south)  -- (t3.north) ;
    \draw [->] (o7.south)  -- (t7.north) ;
    \draw [->] (o10.south) -- (t10.north) ;
    \draw [->] (o25.south) -- (t25.north) ;
    \draw [->] (o50.south) -- (t50.north) ;

    \node(b3)   at (0 , -1.5) {3}  ;
    \node(b7)   at (1 , -1.5) {7}  ;
    \node(b50)  at (2 , -1.5) {50} ;
    \node(b10)  at (3 , -1.5) {10} ;
    \node(b25)  at (4 , -1.5) {25} ;

@@

    \draw[-] (e50.south) -- ++(0.5,-0.75) ;
    \draw[-] (e10.south) -- ++(-1 ,-1.5  ) ;
    \draw[-] (e7.south)  -- ++(1.5,-2.25) ;
    \draw[-] (e3.south)  -- ++(2  , -3 ) ;
    \draw[-] (e25.south) -- ++(-2 , -3 ) ;

    % \node(r40)  [circle, inner sep=0pt, fill=white, anchor=center] at (2.5 , -3.75) {40} ;
    % \node(r280) [circle, inner sep=0pt, fill=white, anchor=center] at (2   , -4.5) {280} ;
    % \node(r255) [circle, inner sep=0pt, fill=white, anchor=center] at (2.5   , -5.25) {255} ;

    % \draw[->] (e50) -- (r40) ;
    % \draw[->] (e10) -- (r40) ;

    \node at (2, -6.5) {$765$} ;

    \node at (6, 0.7) {\parbox{3cm}{\subcaption{Filter        \hfill \; \label{countdown-filter}}}} ;
    \node at (6,-0.8) {\parbox{3cm}{\subcaption{Permutation   \hfill \; \label{countdown-permutation}}}} ;
    \node at (6,-2.3) {\parbox{3cm}{\subcaption{Operators     \hfill \; \label{countdown-operators}}}} ;
    \node at (6,-4.8) {\parbox{3cm}{\subcaption{Parenthesising\hfill \; \label{countdown-parens}}}} ;
  \end{tikzpicture}
  \caption{The components of a transformation which makes up a Countdown
    candidate solution}
\end{figure}
